DATA 621 - Business Analytics and Data Mining

### 2020-11-22 HW5/HW5-Draft.Rmd
Think I'm done my section

`STARS` is especially sparse, but as noted in the assignment, this may be an
indication in and of its own. It is reasonable to assume that the vinters of a
good wine want it to be rated. If they do not submit it for rating, that may be
an indication of their lack of faith in the wine. How to factor this into the
analysis will be decided individually by the modelers in this assignment. The
other missing variables are all less than 10%, and their handling via imputation
or otherwise will be done on a model-by-model basis as well.

@@

Here too, `AcidIndex` and `LabelAppeal` look very similar to their
pre-imputation distribution. What stands out is `STARS`. Both the Poisson and
the negative binomial models are either unimodal or have to consecutive values
sharing the mode, due to their inherent nature as discrete disctibutions. What
is seen here is that 1 star is empirically less common than 0 (unrated) or 2
stars. On the one hand, this could simply be noise (process variance) or
parameter error (finite sample size). On the other, it could indicate the need
for a zero-inflated version of the counting distributions.

@@

\small
```{r m1PTable}
# P1:Print results. This needed to ne in its own section so that the LaTeX
# commands to change the text size can be wrapped around it.
kable(summary(m1PFit$finalModel)$coefficients,
      caption = "Model 1 Poisson Regression Output")
```
\normalsize

@@

```{r m1NBTrain, cache=0}
# NB1: There is no built-in AIC stepping in caret, so using basic glm.nb and
# then calling stepAIC on saturated model
glmc <- glm.control(maxit = 40, epsilon = 1e-8)
set.seed(72)
m1NBFitStart <- glm.nb(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                         AcidIndex * FixedAcidity * VolatileAcidity * pH +
                         Rated:STARS + LabelAppeal:Rated +
                         LabelAppeal:Rated:STARS - INDEX - STARS,
                       data = m1trnImp, control = glmc, link = log)

m1NBFit <- stepAIC(m1NBFitStart, direction = 'both', trace = 0)

>>>>

`STARS` is especially sparse, but as noted in the assignment, this may be an
indication in and of its own. It is reasonable to assume that the vintners of a
good wine want it to be rated. If they do not submit it for rating, that may be
an indication of their lack of faith in the wine. How to factor this into the
analysis will be decided individually by the modelers in this assignment. The
other missing variables are all less than 10%, and their handling via imputation
or otherwise will be done on a model-by-model basis as well.

@@

Here too, `AcidIndex` and `LabelAppeal` look very similar to their
pre-imputation distribution. What stands out is `STARS`. Both the Poisson and
the negative binomial models are either unimodal or have to consecutive values
sharing the mode, due to their inherent nature as discrete distributions. What
is seen here is that 1 star is empirically less common than 0 (unrated) or 2
stars. On the one hand, this could simply be noise (process variance) or
parameter error (finite sample size). On the other, it could indicate the need
for a zero-inflated version of the counting distributions.

@@

\small
```{r m1PTable}
# P1:Print results. This needed to be in its own section so that the LaTeX
# commands to change the text size can be wrapped around it.
kable(summary(m1PFit$finalModel)$coefficients,
      caption = "Model 1 Poisson Regression Output")
```
\normalsize

@@

```{r m1NBTrain}
# NB1: There is no built-in AIC stepping in caret, so using basic glm.nb and
# then calling stepAIC on saturated model. Once done, investigated some one-off
# possible enhancements due to issues with glm.nb
# See https://stackoverflow.com/questions/11749977/why-does-glm-nb-throw-a-missing-value-error-only-on-very-specific-inputs
# For speed, only final called model is evaluated.
set.seed(872)
m1NBFitStart <- glm.nb(TARGET ~ . + FreeSulfurDioxide:TotalSulfurDioxide +
                         AcidIndex * FixedAcidity * VolatileAcidity * pH +
                         Rated:STARS + LabelAppeal:Rated +
                         LabelAppeal:Rated:STARS - INDEX - STARS,
                       data = m1trnImp, link = log)
m1NBFitStep <- stepAIC(m1NBFitStart, direction = 'both', trace = 0)

# Last call from automated procedure
# TARGET ~ FixedAcidity + VolatileAcidity + Chlorides + FreeSulfurDioxide + 
#     TotalSulfurDioxide + pH + Sulphates + Alcohol + LabelAppeal + 
#     AcidIndex + Rated + FreeSulfurDioxide:TotalSulfurDioxide + 
#     FixedAcidity:AcidIndex + VolatileAcidity:AcidIndex + Rated:STARS + 
#     LabelAppeal:Rated + LabelAppeal:Rated:STARS

# Removing VolatileAcidity improved the AIC

m1NBFit <- glm.nb(formula = TARGET ~ FixedAcidity + Chlorides +
                    FreeSulfurDioxide + TotalSulfurDioxide + pH + Sulphates +
                    Alcohol + LabelAppeal + AcidIndex + Rated +
                    FreeSulfurDioxide:TotalSulfurDioxide +
                    FixedAcidity:AcidIndex + VolatileAcidity:AcidIndex +
                    Rated:STARS + LabelAppeal:Rated + LabelAppeal:Rated:STARS,
                  data = m1trnImp, link = log)
